---
title: "Hotel Reviews"
author: "Zhichao Hu, Hui Wang, and Junjie Yang"
date: "November 30, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(ggthemes)
library(faraway)
library(lmtest) 
library(MASS) 
library(leaps) # for regsubsets()
library(boot) # for cv.glm()
```

# EDA of the dataset
## load data
```{r}
hotel_reviews <- read_csv("Hotel_Reviews.csv")
```

## date range of all reviews
```{r}
min(mdy(hotel_reviews$Review_Date))
max(mdy(hotel_reviews$Review_Date))
```

## unique hotels in dataset
There are two hotel with the same name but different addresses; address should be used as a unique identifier.
```{r}
hotel_reviews$Hotel_Name %>% unique() %>% length()
hotel_reviews$Hotel_Address %>% unique() %>% length()
```

## summarise related columns to create predictors
```{r}
hotel_agg <- hotel_reviews %>% group_by(Hotel_Address) %>% 
  summarise(name=first(Hotel_Name), 
            review_t=mean(Total_Number_of_Reviews), # t stands for total
            review_n=mean(Review_Total_Negative_Word_Counts), # n stands for negtive
            review_p=mean(Review_Total_Positive_Word_Counts), # p stands for positive
            review_m=mean(Additional_Number_of_Scoring), # m stands for missing
            reviewer_exp=mean(Total_Number_of_Reviews_Reviewer_Has_Given), #exp stands for experience
            score=mean(Average_Score))
colnames(hotel_agg)[1] <- "address"
```

# dataset overview
```{r}
#dim(hotel_agg)
summary(hotel_agg)
sd(hotel_agg$score)
```

## score histgram

The average scores are not prefectly normal.
```{r}
hotel_agg %>% ggplot(aes(score))+geom_histogram(aes(y=..density..), binwidth=0.1, color="blue", fill="light blue")+
  geom_density(color="red", size=1, fill="red", alpha=0.2)+theme_bw()
```

## remove an outlier with the score of 5.2

```{r}
OutVals = boxplot(hotel_agg$score)$out
```

```{r}
OutVals
which(hotel_agg$score < 5.5)
```

```{r}
#keep records with score greater than 5.5
hotel_agg1 <- hotel_agg %>% filter(score>5.5)
#hotel_agg1=hotel_agg[ -which(hotel_agg$score < 5.5), ] # remove the #1444 hotel with the score of 5.2

hotel_agg1 %>% ggplot(aes(score))+geom_histogram(aes(y=..density..), binwidth=0.1, color="blue", fill="light blue")+
  geom_density(color="red", size=1, fill="red", alpha=0.2)+theme_bw()
#dim(hotel_agg1)
```

One hotel with the lowest score is removed. This hotel has much fewer total number of reviews than the others, which indicates this may be a new hotel.

```{r}
#the removed hotel with lowest score
hotel_agg %>% filter(score<5.5) %>% knitr::kable(align="c")
```

## check predictors

Two predictors, review_t and review_m, are not normally distributed. Both variables are related to amount of reviews.

```{r}
par(mfrow = c(2,3))
hist(hotel_agg1$review_t, main = NULL, ylab = NULL)
hist(hotel_agg1$review_n, main = NULL, ylab = NULL)
hist(hotel_agg1$review_p, main = NULL, ylab = NULL)
hist(hotel_agg1$review_m, main = NULL, ylab = NULL)
hist(hotel_agg1$reviewer_exp, main = NULL, ylab = NULL)
```

# linear model of averaged predictors
## build linear model
Average score of each hotel is the response.
```{r}
lmod <- lm(score~review_t+review_n+review_p+review_m+reviewer_exp, hotel_agg1)
summary(lmod)
```

## model diagnosis

### transformation of response

Try to identify a transformation using Boxcox. The nearest integer is 3, so we consider a transformation of the fitted value with lambda = 3.

```{r}
# Box-cox transformation of response
boxcox(lmod, lambda = seq(1,5,0.1), plotit = TRUE)
```

```{r}
# create new column with transformed response
hotel_agg1 <- hotel_agg1 %>% mutate(scoreCube=(hotel_agg1$score)^3)

# fit a linear model with transformed score as the new response
lmod_y = lm(scoreCube ~ review_t + review_n + review_p + review_m + reviewer_exp, hotel_agg1)
summary(lmod_y)
```

### transformation of two predictors

```{r}
# create new columns of transformed predictors
#hotel_agg1 <- hotel_agg1 %>% mutate(review_t1 = hotel_agg1$review_t^(1/3), review_m1 = hotel_agg1$review_m^(1/3))
hotel_agg1 <- hotel_agg1 %>% mutate(review_t1 = log(hotel_agg1$review_t), review_m1 = log(hotel_agg1$review_m))

# all predictors at this point look normally distributed
par(mfrow = c(2,3))
hist(hotel_agg1$review_t1, main = NULL, ylab = NULL)
hist(hotel_agg1$review_n, main = NULL, ylab = NULL)
hist(hotel_agg1$review_p, main = NULL, ylab = NULL)
hist(hotel_agg1$review_m1, main = NULL, ylab = NULL)
hist(hotel_agg1$reviewer_exp, main = NULL, ylab = NULL)
```

```{r}
# Model with predictors transformed

lmod_x = lm(score ~ review_t1 + review_n + review_p + review_m1 + reviewer_exp, hotel_agg1)
summary(lmod_x)
```

### transformation of response and two predictors

```{r}
# Model with both response and predictors transformed

lmod_xy = lm(scoreCube ~ review_t1 + review_n + review_p + review_m1 + reviewer_exp, hotel_agg1)
summary(lmod_xy)
```

### check error assumption

#### constant variance assumption

##### initial model

Plot the residuals against fitted value and predictors.
Choose review_t and review_m, to take F-test and reject the null hypothesis based on the p-value.
Review_t and review_m are related to the number of reviews or scores of hotels. The hotels who have a small amout of reviwes have larger residuals. 

The other residuals variances are constant. 
```{r}
par(mfrow=c(2,3))
plot(lmod$fitted.values,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg1$review_t,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg1$review_n,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg1$review_p,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg1$review_m,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg1$reviewer_exp,residuals(lmod))
abline(h=0, col = 'red')
```

```{r}
var.test(residuals(lmod)[hotel_agg1$review_t>1000], residuals(lmod)[hotel_agg1$review_t<1000])
var.test(residuals(lmod)[hotel_agg1$review_p>28], residuals(lmod)[hotel_agg1$review_p<28])
var.test(residuals(lmod)[hotel_agg1$review_m>200], residuals(lmod)[hotel_agg1$review_m<200])
```

##### model with transformed response
```{r}
par(mfrow=c(2,3))
plot(lmod_y$fitted.values,residuals(lmod_y))
abline(h=0, col = 'red')
plot(hotel_agg1$review_t,residuals(lmod_y))
abline(h=0, col = 'red')
plot(hotel_agg1$review_n,residuals(lmod_y))
abline(h=0, col = 'red')
plot(hotel_agg1$review_p,residuals(lmod_y))
abline(h=0, col = 'red')
plot(hotel_agg1$review_m,residuals(lmod_y))
abline(h=0, col = 'red')
plot(hotel_agg1$reviewer_exp,residuals(lmod_y))
abline(h=0, col = 'red')
```

##### model with transformed predictors

```{r}
par(mfrow=c(2,3))
plot(lmod_x$fitted.values,residuals(lmod_x))
abline(h=0, col = 'red')
plot(hotel_agg1$review_t1,residuals(lmod_x))
abline(h=0, col = 'red')
plot(hotel_agg1$review_n,residuals(lmod_x))
abline(h=0, col = 'red')
plot(hotel_agg1$review_p,residuals(lmod_x))
abline(h=0, col = 'red')
plot(hotel_agg1$review_m1,residuals(lmod_x))
abline(h=0, col = 'red')
plot(hotel_agg1$reviewer_exp,residuals(lmod_x))
abline(h=0, col = 'red')
```

Performe variance test at places where initial model (lmod) showes deficiency, both tests produce greater p values than before.
```{r}
var.test(residuals(lmod_x)[hotel_agg1$review_t1>log(1000)], residuals(lmod_x)[hotel_agg1$review_t1<log(1000)])
var.test(residuals(lmod_x)[hotel_agg1$review_m1>log(200)], residuals(lmod_x)[hotel_agg1$review_m1<log(200)])
```

##### model with transformed response and predictors
```{r}
par(mfrow=c(2,3))
plot(lmod_xy$fitted.values,residuals(lmod_xy))
abline(h=0, col = 'red')
plot(hotel_agg1$review_t1,residuals(lmod_xy))
abline(h=0, col = 'red')
plot(hotel_agg1$review_n,residuals(lmod_xy))
abline(h=0, col = 'red')
plot(hotel_agg1$review_p,residuals(lmod_xy))
abline(h=0, col = 'red')
plot(hotel_agg1$review_m1,residuals(lmod_xy))
abline(h=0, col = 'red')
plot(hotel_agg1$reviewer_exp,residuals(lmod_xy))
abline(h=0, col = 'red')
```

#### normality assumption

The QQ-plot looks heavy-tailed and the p-value of Shapiro-Wilk normality test is smaller than 0.05 (H0: residuals are normally distributed). Since there are many data points, if the model passes other tests, the normality violation may not be detrimental.

```{r}
qqnorm(residuals(lmod_x),ylab="Residuals",main="QQ plot")
qqline(residuals(lmod_x),col="blue")
```

```{r}
shapiro.test(residuals(lmod_x))
```

```{r}
hist(residuals(lmod_x), breaks = 50)
```

### multicolliearity - Variance Inflation Factor

The max Variance Inflation Factor is smaller than 10 and the average of VIF is about 3. We think the predictors have no multicolliearity.

```{r}
x = model.matrix(lmod_x)[, -1]
vif(x)
mean(vif(x))
```

### Jackknife residuals: Outlier

Bonferroni-corrected criteria here rules out an outlier.

```{r}
nrow(hotel_agg1)
```

```{r}
qt(.025/1492, 1485)
```

```{r}
stud = rstudent(lmod_x)
jackres = stud*(1485/(1486-stud^2))^0.5
head(jackres[order(abs(stud), decreasing = T)])
```

The removed hotel here failed the Bonferroni-corrected criteria. It is a hotel with fewer total number of reviews and a high score.
```{r}
hotel_agg1[1017,c(1:8)] %>% knitr::kable()

hotel_agg2 <- hotel_agg1[-1017,] # subset hotel_agg1 to remove the outlier
```

```{r}
lmod_x1 = lm(score~review_t1+review_n+review_p+review_m1+reviewer_exp, hotel_agg2)
summary(lmod_x1)
```

### influential observations - Cook's D

It appears that all Cook's D values are smaller than 1. We remove the observation with the largest Cook's D and creat a new model. We consider the observation on the upper right a influential data point: its Cook's D value is much greater than the rest of the points.

```{r}
cook = cooks.distance(lmod_x1)
halfnorm(cook, 1, ylab = "Cook's distance")
```

The removed hotel here has much fewer total reviews and a high score.
```{r}
hotel_agg2[1410,c(1:8)] %>% knitr::kable()

hotel_agg3 <- hotel_agg2[-1410,] # subset hotel_agg2 to remove the outlier
```

```{r}
lmod_x2 = lm(score~review_t1+review_n+review_p+review_m1+reviewer_exp, hotel_agg3)
summary(lmod_x2)
```

## model selection

Targeted model is the one with transformed predictors (lmod_x2) having outliers removed.

### forward search

```{r}

out.null = lm(score ~ 1, hotel_agg3)
out.full = formula(lmod_x2)

out_f = regsubsets(out.full, data = hotel_agg3, method = 'forward', nvmax = 5)
out_f0 = summary(out_f)
out_f0$outmat
```

```{r}
bic = out_f0$bic
cat("BIC:", bic)
```

```{r}
adjr2=out_f0$adjr2
cat("adjusted R^2:", adjr2)
```

```{r}
#Best model in terms of both adjusted R-squared and bic is the full model 
which.min(out_f0$bic) 
which.max(out_f0$adjr2)
```

```{r}
plot(c(1, 2, 3, 4, 5), bic, xlab="predictors (not including intercept)")
```

```{r}
plot(out_f, scale="adjr2", main=expression(adjusted~R^2))
```

### early stopping forward selection using BIC

```{r}
n = nrow(hotel_agg3)

out.forward = step(out.null, scope = list(lower = ~1, upper = out.full), 
                   k = log(n), direction = "forward", trace = FALSE)
out.forward$coefficients

```

## 5 Fold Cross Validation for lmod_x2
methond 1
```{r}
set.seed(1)
k=5
fold=sample(1:k,nrow(hotel_agg3),replace=TRUE)

kfold.rmse=1:k # we will have 5 RMSEs to fill this with later
for(i in 1:k){
  test=hotel_agg3[fold==i,] # test set is the ith group for the ith iteration
  train=hotel_agg3[fold!=i,]# training set is all the other groups
  model=lm(score~review_t1+review_n+review_p+review_m1+reviewer_exp,train)
  pred.y=predict(model,test)
  rmse=sqrt(mean((test$score-pred.y)^2))
  
  kfold.rmse[i]=rmse # store current iteration RMSE into ith position of kfold.rmse
}

kfold.rmse # show our RMSEs for each iteration
mean(kfold.rmse) #avg rmse
```
method 2
```{r}
set.seed(9)
# class example of K fold CV
mse_avg_1=cv.glm(data=hotel_agg3, glm(score ~ review_t1 + review_n + review_p + review_m1 + reviewer_exp, data=hotel_agg3), K=5)$delta[1]
mse_avg_1^(1/2)
```

## 5 Fold Cross Validation for lmod_x1_noexp (manually removed the least significant predictor)
```{r}
#If we ddecide to get rid of variable exp based on forward selection
lmod_x3_noexp = lm(score~review_t1+review_n+review_p+review_m1, hotel_agg3)
summary(lmod_x3_noexp)
```

method 1
```{r}
set.seed(1)
k=5
fold=sample(1:k,nrow(hotel_agg3),replace=TRUE)

kfold.rmse=1:k # we will have 5 RMSEs to fill this with later
for(i in 1:k){
  test=hotel_agg3[fold==i,] # test set is the ith group for the ith iteration
  train=hotel_agg3[fold!=i,]# training set is all the other groups
  model1=lm(score~review_t1+review_n+review_p+review_m1,train)
  pred.y1=predict(model1,test)
  rmse=sqrt(mean((test$score-pred.y1)^2))
  
  kfold.rmse[i]=rmse # store current iteration RMSE into ith position of kfold.rmse
}

kfold.rmse # show our RMSEs for each iteration
mean(kfold.rmse) #avg rmse
```
method 2
```{r}
set.seed(2)
# class example of K fold CV
mse_avg_2=cv.glm(data=hotel_agg3, glm(score ~ review_t1 + review_n + review_p + review_m1, data=hotel_agg3), K=5)$delta[1]
mse_avg_2^(1/2) # average rmse
```
# summary

This section highlights a few important findings from the previous analysis.

## three removed outliers

Using different techniques, we identified and removed three outliers. These hotel are the one with much fewer total number of reviews compared to other hotels in this dataset in general. This indicates that these may be new hotels and their scores are not stable yet.

```{r}
hotel_agg %>% filter(name=="Hotel Liberty"|name=="Hotel Gallitzinberg"|name=="Hotel Silver") %>% 
  knitr::kable()

```

Compare with other hotel with a lot more total number of reviews.

```{r}
hotel_reviews %>% group_by(Hotel_Address) %>% summarise(name=first(Hotel_Name), count=n()) %>% 
  arrange(desc(count)) %>% dplyr::select(name, count) %>% 
  head() %>% #select() may get masked by another package therefore specify dplyr
  knitr::kable()
```

## comparison of residual variance against two predictors for different models
```{r}
par(mfcol=c(2,4))
plot(hotel_agg1$review_t,residuals(lmod), col="dark blue", xlab="review_t", ylab="residuals", main="lmod")
abline(h=0, col = 'red')
plot(hotel_agg1$review_m,residuals(lmod), xlab="review_m", ylab="residuals", main="lmod")
abline(h=0, col = 'red')
plot(hotel_agg1$review_t,residuals(lmod_y), col="dark blue", xlab="review_t", ylab="residuals", main="lmod_y")
abline(h=0, col = 'red')
plot(hotel_agg1$review_m,residuals(lmod_y), xlab="review_m", ylab="residuals", main="lmod_y")
abline(h=0, col = 'red')
plot(hotel_agg1$review_t1,residuals(lmod_x), col="dark blue", xlab="log(review_t)", ylab="residuals", main="lmod_x")
abline(h=0, col = 'red')
plot(hotel_agg1$review_m1,residuals(lmod_x), xlab="log(review_m)", ylab="residuals", main="lmod_x")
abline(h=0, col = 'red')
plot(hotel_agg1$review_t1,residuals(lmod_xy), col="dark blue", xlab="log(review_t)", ylab="residuals", main="lmod_xy")
abline(h=0, col = 'red')
plot(hotel_agg1$review_m1,residuals(lmod_xy), xlab="log(review_m)", ylab="residuals", main="lmod_xy")
abline(h=0, col = 'red')
```
