---
title: "Hotel Reviews"
author: "Zhichao Hu, Hui Wang, and Junjie Yang"
date: "11/29/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
knitr::opts_chunk$set(echo = FALSE)
library(faraway)
library(tidyverse)
library(lubridate)
library(ggthemes)
library(lmtest)
```

# load data
```{r}
hotel_reviews <- read_csv("Hotel_Reviews.csv")
```

# date range of all reviews
```{r}
min(mdy(hotel_reviews$Review_Date))
max(mdy(hotel_reviews$Review_Date))
```

# unique hotels in dataset
There are two hotel with the same name but different addresses; address should be used as a unique identifier.
```{r}
hotel_reviews$Hotel_Name %>% unique() %>% length()
hotel_reviews$Hotel_Address %>% unique() %>% length()
```

# hotels with most number of reviews
```{r}
hotel_reviews %>% group_by(Hotel_Address) %>% summarise(name=first(Hotel_Name), count=n()) %>% 
  arrange(desc(count)) %>% select(name, count)
```

# summarise related columns to create predictors
```{r}
hotel_agg <- hotel_reviews %>% group_by(Hotel_Address) %>% 
  summarise(name=first(Hotel_Name), 
            review_total=mean(Total_Number_of_Reviews), 
            review_n=mean(Review_Total_Negative_Word_Counts),
            review_p=mean(Review_Total_Positive_Word_Counts), 
            review_m=mean(Additional_Number_of_Scoring),
            reviewer_exp=mean(Total_Number_of_Reviews_Reviewer_Has_Given),
            score=mean(Average_Score))
colnames(hotel_agg)[1] <- "address"
```

# score histgram
```{r}
hotel_agg %>% ggplot(aes(score))+geom_histogram(aes(y=..density..), binwidth=0.1, color="blue", fill="light blue")+
  geom_density(color="red", size=1, fill="red", alpha=0.2)+theme_bw()
```

# build linear model
```{r}
lmod <- lm(score~review_total+review_n+review_p+review_m+reviewer_exp, hotel_agg)
```

```{r}
summary(lmod)
```

# Checking Error Assumption

## Constant variance assumption

```{r}
par(mfrow=c(2,3))
plot(lmod$fitted.values,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg$review_total,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg$review_n,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg$review_p,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg$review_m,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg$reviewer_exp,residuals(lmod))
abline(h=0, col = 'red')
```

## Normality assumption

```{r}
qqnorm(residuals(lmod),ylab="Residuals",main="")
qqline(residuals(lmod),col='blue')
shapiro.test(residuals(lmod))
```

## Correlated errors

```{r}
dwtest(score~review_total+review_n+review_p+review_m+reviewer_exp, data = hotel_agg)
```

# Multicolliearity

```{r}
x = model.matrix(lmod)[, -1]
vif(x)
ave(vif(x))
```
