---
title: "Hotel Reviews"
author: "Zhichao Hu, Hui Wang, and Junjie Yang"
date: "November 30, 2019"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(ggthemes)
library(faraway)
library(lmtest)
```
# EDA of the dataset
## load data
```{r}
hotel_reviews <- read_csv("Hotel_Reviews.csv")
```
## date range of all reviews
```{r}
min(mdy(hotel_reviews$Review_Date))
max(mdy(hotel_reviews$Review_Date))
```

## unique hotels in dataset
There are two hotel with the same name but different addresses; address should be used as a unique identifier.
```{r}
hotel_reviews$Hotel_Name %>% unique() %>% length()
hotel_reviews$Hotel_Address %>% unique() %>% length()
```

## hotels with most number of reviews
```{r}
hotel_reviews %>% group_by(Hotel_Address) %>% summarise(name=first(Hotel_Name), count=n()) %>% 
  arrange(desc(count)) %>% select(name, count)

```

## summarise related columns to create predictors
```{r}
hotel_agg <- hotel_reviews %>% group_by(Hotel_Address) %>% 
  summarise(name=first(Hotel_Name), 
            review_t=mean(Total_Number_of_Reviews), # t stands for total
            review_n=mean(Review_Total_Negative_Word_Counts), # n stands for negtive
            review_p=mean(Review_Total_Positive_Word_Counts), # p stands for positive
            review_m=mean(Additional_Number_of_Scoring), # m stands for missing
            reviewer_exp=mean(Total_Number_of_Reviews_Reviewer_Has_Given), #exp stands for experience
            score=mean(Average_Score))
colnames(hotel_agg)[1] <- "address"
```

## score histgram

The average scores are not prefectly normal.
```{r}
hotel_agg %>% ggplot(aes(score))+geom_histogram(aes(y=..density..), binwidth=0.1, color="blue", fill="light blue")+
  geom_density(color="red", size=1, fill="red", alpha=0.2)+theme_bw()
```

# linear model of averaged predictors
## build linear model
Average score of each hotel is the response.
```{r}
lmod <- lm(score~review_t+review_n+review_p+review_m+reviewer_exp, hotel_agg)
summary(lmod)
```

## model diagnosis
### check error assumption
#### constant variance assumption

Plot the residuals against fitted value and predictors.
Choose review_t and review_m, to take F-test and reject the null hypothesis based on the p-value.
Review_t and review_m are related to the number of reviews or scores of hotels. The hotels who have a small amout of reviwes have larger residuals. 

The other residuals variances are constant. 
```{r}
par(mfrow=c(2,3))
plot(lmod$fitted.values,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg$review_t,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg$review_n,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg$review_p,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg$review_m,residuals(lmod))
abline(h=0, col = 'red')
plot(hotel_agg$reviewer_exp,residuals(lmod))
abline(h=0, col = 'red')

var.test(residuals(lmod)[hotel_agg$review_t>2000], residuals(lmod)[hotel_agg$review_t<2000])
var.test(residuals(lmod)[hotel_agg$review_p>28], residuals(lmod)[hotel_agg$review_p<28])
var.test(residuals(lmod)[hotel_agg$review_m>250], residuals(lmod)[hotel_agg$review_m<250])
```

#### normality assumption

The QQ-plot looks heavy-tailed and the p-value of Shapiro-Wilk normality test is smaller than 0.05.
But from the histgram plot, it looks normal without lowest points around -2.0.

```{r}
qqnorm(residuals(lmod),ylab="Residuals",main="QQ plot")
qqline(residuals(lmod),col="blue")
shapiro.test(residuals(lmod))

hist(residuals(lmod), breaks = 100)

```

#### correlated errors

The p-value of DW test is much smaller than 0.05, we need reject the null hypothesis. Why???
Do we still need to check the correlated errors?

```{r}
dwtest(score~review_t+review_n+review_p+review_m+reviewer_exp, data = hotel_agg)
```

### multicolliearity

The max Variance Inflation Factor is smaller than 10 and the average of VIF is 2. We think the predictors are not multicolliearity.

```{r}
x = model.matrix(lmod)[, -1]
vif(x)
mean(vif(x))
```


# liner model of a single hotel
## Prepare subset
Choose a hotel with most number of reviews to explore other individual characteristics of reviewers as predictors
```{r}
#subset the intial dataframe to a single hotel
hotel_bri <- hotel_reviews %>% filter(Hotel_Name=="Britannia International Hotel Canary Wharf") %>% 
  select(review_t=Total_Number_of_Reviews,
         review_n=Review_Total_Negative_Word_Counts,
         review_p=Review_Total_Positive_Word_Counts,
         review_m=Additional_Number_of_Scoring,
         reviewer_exp=Total_Number_of_Reviews_Reviewer_Has_Given,
         score_i=Reviewer_Score) # i stands for individual

```

## individual score histgram

The individual scores are not normal.
```{r}
hotel_bri %>% ggplot(aes(score_i))+geom_histogram(aes(y=..density..), binwidth=0.1, color="blue", fill="light blue")+
  geom_density(color="red", size=1, fill="red", alpha=0.2)+theme_bw()
```

## build linear model
Each individual score (Reviewer_Score) is the response.
```{r}
lmod_bri <- lm(score_i~review_t+review_n+review_p+review_m+reviewer_exp, hotel_bri)
```

```{r}
summary(lmod_bri)
```

```{r}

```


